TEMPERATURES AND METALLICITIES OF M DWARFS IN THE APOGEE SURVEY

### 2019-09-10 paper/draft.tex
add acknowledgments

% \usepackage{draftwatermark}
% \SetWatermarkScale{3}
% \SetWatermarkLightness{.7}

@@

\subsection{Temperature/Metallicity Model \label{subsec:mann_results}}
2
\begin{figure}
	\includegraphics[width=\linewidth]{crv_test_teff.png}
	\includegraphics[width=\linewidth]{crv_test_fe_h.png}
	\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (top), and leave-one-out cross validation (bottom). Sources with strong rotational broadening (2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles. Predictive accuracy, as computed by the scatter in cross validation is 77K in temperature, and 0.09 dex in metallicity.} 
	\label{fig:mann_validation}
\end{figure}

@@

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.9\linewidth]{aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 1,702 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{center}
\end{figure*}

@@

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Melissa Ness (Columbia), Kevin Covey (WWU), Diogo Souto (Observatário Nacional/MCTI) and Keivan Stassun (Vanderbuilt) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
This project was partially supported by
the US National Aeronautics and Space Administration (NASA grant NNX12AI50G),
the US National Science Foundation (NSF grant AST-1517237),
and the Moore--Sloan Data Science Environment at NYU.
A.J.B. acknowledges funding support from the National Science Foundation under award No. AST-1517177.
This work is supported by the SDSS Faculty and Student Team (FAST) initiative.

@@

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff1.png} 
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff2.png}
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallicities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise.}
	\label{fig:demo_teff}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh1.png}
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh2.png}
	\end{center}
\end{figure*}

\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, $\feh=-0.03$\,dex; jackknife computed error at each pixel is shown in red.} \label{fig:demo_feh}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=12cm]{Spectral_Sequence_1.png}
	\includegraphics[width=12cm]{Spectral_Sequence_2.png}
	\includegraphics[width=12cm]{Spectral_Sequence_3.png}
	\end{center}
	\caption{Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of APOGEE spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure*}

%---------------------------
\begin{figure*}[]
	\begin{center}
	\includegraphics[width=16cm]{derivative_jackknife_spt.png}
	\end{center}
	\caption{Derivative plots for spectral type model taken at the median training spectral type, SPT$=3$; jackknife computed error at each pixel is shown in red.} 
	\label{fig:west_derivative}
\end{figure*}

>>>>

@@

\subsection{Temperature/Metallicity Model \label{subsec:mann_results}}

\begin{figure}
	\includegraphics[width=\linewidth]{crv_test_teff.png}
	\includegraphics[width=\linewidth]{crv_test_fe_h.png}
	\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test (top), and leave-one-out cross validation (bottom). Sources with strong rotational broadening (2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380), as identified by visual inspection are marked with red circles. Predictive accuracy, as computed by the scatter in cross validation is 77K in temperature, and 0.09 dex in metallicity.} 
	\label{fig:mann_validation}
\end{figure}

@@

\begin{figure*}
\begin{center}
	\includegraphics[width=.9\linewidth]{aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 1,702 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{center}
\end{figure*}

@@

%%==========================================================================================
\acknowledgements
We would like to acknowledge Hans Walter Rix (MPIA), Derek Homeier (Universit{\"a}t Heidelberg), Wolfgang Bradner (MPIA), Anna-Christina Eilers (MPIA), Melissa Ness (Columbia), Kevin Covey (WWU), Diogo Souto (Observatário Nacional/MCTI), Keivan Stassun (Vanderbuilt), Anthony Brown (Leiden), Aida Behmard (Caltech) and Christopher Theissen (UCSD) for constructive discussions in the process of this project, as well as Bertrand Goldman (MPIA) and those who have supported the internship program at the Max Planck Institute f{\"u}r Astronomie for providing JB with funding and hospitality.
This project was partially supported by
the US National Aeronautics and Space Administration (NASA grant NNX12AI50G),
the US National Science Foundation (NSF grant AST-1517237),
and the Moore--Sloan Data Science Environment at NYU.
A.J.B. acknowledges funding support from the National Science Foundation under award No. AST-1517177.
This work is supported by the SDSS Faculty and Student Team (FAST) initiative.

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff1.png} 
	\end{center}
\end{figure*}

\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff2.png}
	\end{center}
\end{figure*}

\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_teff3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying temperatures, and similar metallicities. \textit{Third panel of each plot:} Derivative of \thecannon\ model with respect to temperature, taken at the median training temperature, T$_{\rm eff}=3463$K; error estimate computed using a jackknife statistic at each pixel is marked in red, making it possible to distinguish which features vary significantly with change in spectral type, and which are likely due to noise.}
	\label{fig:demo_teff}
\end{figure*}

%---------------------------
\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh1.png}
	\end{center}
\end{figure*}

\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh2.png}
	\end{center}
\end{figure*}

\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{demo_derivatives_feh3.png}
	\end{center}
	\caption{\textit{Top two panels of each plot:} Mann-trained model for varying metallicities and similar temperatures. \textit{Third panel:} Derivative of \thecannon\ model with respect to metallicity, taken at the median training metallicity, $\feh=-0.03$\,dex; jackknife computed error at each pixel is shown in red.} \label{fig:demo_feh}
\end{figure*}

%---------------------------
\begin{figure*}
	\begin{center}
	\includegraphics[width=12cm]{Spectral_Sequence_1.png}
	\includegraphics[width=12cm]{Spectral_Sequence_2.png}
	\includegraphics[width=12cm]{Spectral_Sequence_3.png}
	\end{center}
	\caption{Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of APOGEE spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure*}

%---------------------------
\begin{figure*}
	\begin{center}
	\includegraphics[width=16cm]{derivative_jackknife_spt.png}
	\end{center}
	\caption{Derivative plots for spectral type model taken at the median training spectral type, SPT$=3$; jackknife computed error at each pixel is shown in red.} 
	\label{fig:west_derivative}
\end{figure*}
